\textbf{BibTrek Prototype: A Graph Visualization Tool and Search Engine for Cybersecurity Papers}

### 2019-07-25 article/article.tex
Phrase reconstruction

\section{Solution}
(Sketch)
#Write a brief introduction. Maybe use the text that I used above but here instead
\subsection{Design}
The BibTrek application was written using the Java programming language mainly due to the fact that it is ubiqutuous on modern-day computing systems. The database module uses Neo4J and requires us to have either a local or remote instance running it. The connection of the JVM to the Neo4J is made using the BOLT protocol on the network port: 7687. The API information is retrieved and parsed in the offered JSON format option due to its lightweight format and overall flexibility. The information in the database server is addressed using Cypher queries. The application was built using the Maven tool and uses the Neo4J driver repository in order to establish a connection with the database. It also uses the JSON repository in order to properly parse the JSON information retrieved in the GET responeses coming from the server. Finally it uses the java.net package in order to establish a connection with the DBLP API, query it and retrieve the response information.

\subsection{Implementation}
At the present time BibTrek only uses the DBLP API to obtain information about the publications. In the current implementation after the user chooses one of the options available to query the database, the user inputs a publication title that is scanned and properly parsed into a DBLP API formated query to the database. The queries are done through the URL link. After the query is sucessfully processed by the DBLP database the BibTrek HTTP module retrieves the response, parses the JSON and displays the information in the user console. After choosing whichever papers are appropriate for its research the system uses its writer module writing the parsed JSON response to a properly named ".nosql" file. The information is properly parsed into a "Cypher" query in order to be stored later in the Neo4J database Every request to the database creates a ".nosql" file that is read every 5 seconds by a thread that communicates with the Neo4J server app and stores the recent written data there. These files are then moved to a "logs" folder in order not to be re-written into the database. An example of a query from our system to the database would be the following. The user chooses the option to query the system by publication title. Let us say he choses the Spectre paper. Because of this a query is properly formated "dblp.org/publ/api?q=Spectre&format=json". In this example we are querying the DBLP database to fetch us all the available Spectre publications "q=Spectre" in the JSON format "format=json". After obtaining the HTTP response and parsing its JSON format the information is displayed to the user. Here every paper with the Spectre title is shown. The user chooses one or more of the papers to add to the database. After choosing the papers the information is then parsed into a cypher query and added to a nosql file. The thread responsible with the Neo4J communication and data storage will query the nosql folder for new files. If a new file is found the most recent data is then stored in the Neo4J communication. This information can then be visually seen by the user using the Neo4J browser. Finally the Neo4J Java thread moves the most recently written file to a logs folder in order for it not to be written again.

>>>>

\section{Solution}
(Sketch)
#Write a brief introduction. Maybe use the text that I used above but here instead
\subsection{Design}
The BibTrek application was written using the Java programming language mainly due to the fact that it is ubiquitous on modern-day computing systems. The database module uses Neo4J and requires us to have either a local or remote instance running it. The connection of the JVM to the Neo4J is made using the BOLT protocol on the network port: 7687. The JSON format was chosen as the way to retrieve the information from the DBLP database using the API due to it being lightweight and having overall great flexibility. The Neo4J database is queried using "
Cypher" which is its standard query language. The application was built using the Maven tool and uses the Neo4J driver and JSON maven repositories. Finally, we use the java.net package in order to establish an HTTP connection with the DBLP API.

\subsection{Implementation}
At the present time, BibTrek only uses the information obtained from querying DBLP API to populate our server. In the current implementation after choosing one of the available options to query the database, the user inputs either an author's name or publication title that is scanned and properly parsed into a query. Queries are done through the composition of a specifically formatted URL link and an HTTP request. After the query is successfully processed by the DBLP database the JSON response is properly parsed and displayed in the terminal console. After choosing whichever papers are appropriate for its research the parsed JSON response is transformed into a Cypher query and written into a file. This file will later be used to create nodes and the relationships between them in our Neo4J database. This file is processed by a thread that periodically searches the current folder for newly written update files and is responsible for storing this information onto the graph database. Once the thread has finished its update responsibilities these files are then moved to a different folder in order not to be re-written into the database. An example execution of a query would be the following. The user starts by choosing the option to query the libraries for a publication by its title. Let us say he chose to query the system for publications about the Spectre attack. Because of this a query is properly formatted in the following way: "https://dblp.org/search/publ/api/?q=Spectre&format=json". The "q=Spectre" parameter in the URL link means that we are querying the system for Spectre subject; "search/publ/api/" means we will be using its API and search for a publication; "&format=json" means we want the fetched data in the JSON format. After obtaining the HTTP response and parsing its JSON the information is then displayed to the user. Here every available publication about the Spectre attack is shown on the console in order for the user to choose one or more of them adding them to the Neo4J database. Afterwards the chosen information is then parsed into a Cypher query and stored. The thread responsible with the Neo4J communication and data storage will search the BibTrek file system for newly added files. If a new file is found the most recent data is then stored in the Neo4J database. The Neo4J Java thread moves the most recently written file to a different folder than the one mentioned before. Finally, the constructed graph can then be observed using the Neo4J browser by the user and infer useful information about the Spectre attack its authors and other related papers.
